### 2010-03-26 docs/architecture/architecture.tex
more documentation...

\subsection{Plane-Parallel Geometry}

\subsection{Full Star / Spherical}

\subsection{Small-scale Flame}

@@

Individual state variables should be indexed using the {\tt variables}
module, with {\tt rho\_comp} referring to the density, {\tt rhoh\_comp}
referring to the enthalpy quantity $(\rho h)$, and {\tt spec\_comp}
referring to the start of the species (partial densities).

@@

In creating the advective fluxes, we need the time-centered velocity
through the faces of the zone---the $x$-velocity on the $x$-edges, the
$y$-velocity on the $y$-edges, etc.\ (see figure~\ref{fig:mac}).  This
type of velocity discretization is termed the MAC velocity (after the
``marker-and-cell'' method for free boundaries in incompressible
flows, Harlow and Welch 1965).

@@

@@

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are listed in table~\ref{tab:variable_keys}.
\begin{table}[h!]
\centering
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density * specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & starting index of the species \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}
\caption{\label{tab:variable_keys} {\tt variables} module common keys}
\end{table}

To find a particular species, a query can be made through the {\tt
  network} module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.
The {\tt variables} module also provides keys for the plotfile
variables and boundary condition types.

>>>>

\subsection{Preparing the Initial Model}

MAESTRO models subsonic flows that are in hydrostatic equilibrium.
The solution in MAESTRO is broken up into a 1-d base state and the 2-
or 3-d full state.  The job of the 1-d base state in the algorithm is
to represent the hydrostatic structure.  The full, Cartesian state
carries the departures from hydrostatic equilibrium.  The underlying
formulation of the low Mach number equations assumes that the base
state is in hydrostatic equilibrium.  At the start of a simulation,
the initial model is read in and taken as the base state.  Therefore,
any initial model needs to already be in hydrostatic equilibrium.

The routines in {\tt MAESTRO/initial\_model/} take a 1-d initial
model and map it onto a uniform grid, at the desired resolution, using
the equation of state in MAESTRO, and using MAESTRO's discretization of
hydrostatic equilibrium.

@@

Individual state variables should be indexed using the integer keys provided 
by the {\tt variables} module (see \S \ref{sec:variables_module}).  For example,
the integer {\tt rho\_comp} will always refer to the density component of the state.

@@

In creating the advective fluxes, we need the time-centered velocity
through the faces of the zone---the $x$-velocity on the $x$-edges, the
$y$-velocity on the $y$-edges, etc.\ (see figure~\ref{fig:mac}).  This
type of velocity discretization is termed the MAC velocity (after the
``marker-and-cell'' method for free boundaries in incompressible
flows \cite{harlowwelch:1965}).

@@

The {\tt eos\_module} provides the interface to the equation of 
state to connect the state variables thermodynamically.  It 
gets the information about the fluid species from the {\tt network}
module (for example, the atomic number, $Z$, and atomic weight, $A$,
of the nuclei).

@@

To find the location of a particular species (for instance, ``carbon-12'')
in the allowed range of {\tt 1:nspec}, you do the following query:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
If the resulting index is {\tt -1}, then the requested species was not
found.

@@

\label{sec:variables_module}

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are listed in table~\ref{tab:variable_keys}.
\begin{table}[h!]
\centering
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density $\times$ specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & first species partial density, $(\rho X_1)$ \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}

\caption{\label{tab:variable_keys} {\tt variables} module common keys}
\end{table}

The species indices are contiguous in the state array, spanning {\tt spec\_comp:spec\_comp-1+nspec}.
To find a particular species, a query can be made through the {\tt
  network} module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.
The {\tt variables} module also provides keys for the plotfile
variables and boundary condition types.

\section{BoxLib Helper Modules}

\subsection{{\tt bl\_types}}

\subsection{{\tt bl\_constants}}
